Open-Set Domain Adaptation through Self-Supervision

### 2022-01-12 Report/Paper_OpenSet.tex

@@

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
%\bibliography{egbib}
}

>>>>

In the computer vision research area large amounts of unlabeled data are available, however the cost of labelling this data is high ~\cite{Csurka2017}. Domain adaptation is one technique that can be used to exploit the unlabeled data by first training a model on labeled data from a different but similar domain (the \textit{source} domain), and then applying this model to the unlabeled data ( the \textit{target} domain). This technique assumes the distribution of both source and target domans are similar and describe the same class labels, also known as the \textit{closed-set} scenario~\cite{Bucci2020}. When applied to real-word scenarios however it is possible that the target domain includes previously unseen classes, known as the \textit{open-set} scenario. These extra class labels in the target domain will cause performance degradation of the classification model and should be identified and isolated. The problem thus consists of two steps: first separating the target domain into known and unknown samples; then conducting domain alignment between the source domain and the known samples of the target domain.

Self-supervised learning can be used to separate the known class samples in the target domain from the unknown samples. Self-supervised learning involves using known ...

@@

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
